\documentclass{CVSoftwareEngineer}

\titlespacing{\section}{0pt}{-10pt}{4pt}

\cvname{Kafetzis, Dimitris Andreas}
\cvjobtitle{Principal Software Engineer}
\cvaddress{Singapore}
\cvlinkedin{\href{https://www.linkedin.com/in/kafetzisd}{linkedin.com/in/kafetzisd}}
\cvgithub{\href{https://github.com/amolofos}{github.com/amolofos}}
\cvmail{kafetzis.dimitris.andreas@gmail.com}

\begin{document}

	\section{\textbf{\cvname}}
	\begin{center}
		\href{mailto:\cvmail}{\cvmail} \space \textbar \space \cvlinkedin \space \textbar \space \cvgithub \\
		Greek working under \textit{Employment Pass} in \cvaddress
	\end{center}
	My experience spans across 10 YoE designing and building heavily transactional, distributed,
	relational database backed systems. The last 3 years I have made a shift on the SRE problem domain.

	\section{Work experience}
	\begin{enumerate}[labelwidth=!, labelindent=0pt, leftmargin=*, rightmargin=15pt]

		\item[] \cvExperience
			{Site Reliabily Engineer (SRE) / Platform Engineer}
			{\href{https://vegasolutions.co}{VegaSolutions} / \href{https://tokkalabs.com}{TokkaLabs} / \href{https://native.org/}{Native} / \href{https://www.rangeprotocol.com/}{RangeProtocol}}
			{Singapore}
			{Nov 2022 - Present}
			{
				\\ Joined as the first dedicated SRE/Platform engineer
				\begin{enumerate}[labelwidth=!, labelindent=0pt, nosep, leftmargin=*]
					\item[\textasteriskcentered] Designed and implemented a cloud architecture reducing
						latency from ~1s to below 500ms.
					\item[\textasteriskcentered] Managed 9 K8s clusters across 3 regions provisioning a region in less than 2 days.
					\item[\textasteriskcentered] Created template integrations for instrumenting nodejs and python services
						against Prometheus, Grafana and Jaeger allowing engineers to investigate issues in a matter of minutes.
					\item[\textasteriskcentered] Refactored helm templates and value files easing maintenance and empowering
						engineers to introduce new services from a couple of days to a few minutes.
				\end{enumerate}
			}

		\item[] \cvExperience
			{Site Reliabily Engineer (SRE)}
			{\href{https://www.bytedance.com/en}{Bytedance}}
			{Singapore}
			{Sept 2021 - Oct 2022 (1yr 1mo)}
			{
				\\ Joined the newly formed SRE team supported the Global E-commerce function of TikTok
				\begin{enumerate}[labelwidth=!, labelindent=0pt, nosep, leftmargin=*]
					\item[\textasteriskcentered] Implemented a Kubernetes sidecar measuring the availability SLI of more than 200 HTTP services.
					\item[\textasteriskcentered] Designed and implemented the MVP version of an incident record tool aiming to reduce the manual bookkeeping activities during oncall cases and build a knowledge base based on them.
				\end{enumerate}
			}

		\item[] \cvExperience
			{Principal Integration Engineer \textbar SRE}
			{\href{https://www.openbet.com/}{OpenBet}}
			{Singapore}
			{Aug 2020 - Sept 2021 (1yr 1mo)}
			{\begin{enumerate}[labelwidth=!, labelindent=0pt, nosep, leftmargin=*]
					\item[\textasteriskcentered] Defined the initial process for an SRE rota across two teams located in multiple locations.
					\item[\textasteriskcentered] Configured prometheus and grafana infrastructure reducing the manual daily SRE monitoring activities.
				\end{enumerate}
			}

		\item[] \cvExperience
			{Principal Software Engineer}
			{\href{https://www.openbet.com/}{OpenBet}}
			{Singapore}
			{Sep 2018 - Jul 2020 (1yr 11mos)}
			{\begin{enumerate}[labelwidth=!, labelindent=0pt, nosep, leftmargin=*]
					\item[\textasteriskcentered] Led a team of 3 engineers hardening the
						funding flow droping incindents from 1 per week to 1 per year.
					\item[\textasteriskcentered] Enhanced the performance of slow database queries reducing
						the number of production incidents due to human design error to zero (0).
					\item[\textasteriskcentered] Migrated 80 million lottery bets to a more robust data model.
				\end{enumerate}
			}

		\item[] \cvExperience
			{Senior Software Engineer}
			{\href{https://www.openbet.com/}{OpenBet}}
			{Singapore}
			{Oct 2015 - Aug 2018 (2yrs 11mos)}
			{
				\begin{enumerate}[labelwidth=!, labelindent=0pt, nosep, leftmargin=*]
					\item[\textasteriskcentered] Owned the data migration of 100 million rows of
						transaction history completed in under 3 hours.
					\item[\textasteriskcentered] Influenced the release process from code to
						production increasing the delivery capacity of the team.
					\item[\textasteriskcentered] Refactored the Ansible deployment scripts
						reducing to zero the release related incidents.
				\end{enumerate}
			}

		\item[]  \cvExperience{Software Engineer}
			{\href{https://www.openbet.com/}{OpenBet}}
			{Athens, Greece}
			{Nov 2012 - Sep 2015 (2 yrs 11mos)}
			{
				\begin{enumerate}[labelwidth=!, labelindent=0pt, nosep, leftmargin=*]
					\item[\textasteriskcentered] Wrote and executed the extraction of
						one billion rows during uptime with no impact to operations.
					\item[\textasteriskcentered] Removed the need for PCI compliance by
						integrating with tokenized credit card providers.
				\end{enumerate}
			}
	\end{enumerate}

	\section{Education}
	\begin{enumerate}[labelwidth=!, labelindent=0pt, leftmargin=*, rightmargin=15pt]
		\item[] Not completed tertiary education \\
			DO, Electrical Engineering and Computer Science, University of Patras, Greece \hfill {\scriptsize Sep 2003 - Jul 2009}
	\end{enumerate}

\end{document}
